\item[{\color{deemph}\scriptsize14}]Norman, D.~\textit{et al.}~(incl. \textbf{APW}), \textit{The Growing Importance of a Tech Savvy Astronomy and Astrophysics Workforce}, 2019 (\arxiv{1910.08376})

\item[{\color{deemph}\scriptsize13}]Nidever, D. L.; \textbf{Price-Whelan,~A.~M.}; Choi, Y.; Beaton, R. L.~\textit{et al.}, \textit{Spectroscopy of the Young Stellar Association Price-Whelan 1: Origin in the Magellanic Leading Arm and Constraints on the Milky Way Hot Halo}, 2019 (\arxiv{1910.05360})

\item[{\color{deemph}\scriptsize12}]\textbf{Price-Whelan,~A.~M.}; Mateu, C.; Iorio, G.; Pearson, S.~\textit{et al.}, \textit{Kinematics of the Palomar 5 stellar stream from RR Lyrae stars}, 2019 (\arxiv{1910.00595})

\item[{\color{deemph}\scriptsize11}]Bonaca, A.; Pearson, S.; \textbf{Price-Whelan,~A.~M.}; Dey, A.~\textit{et al.}, \textit{Variations in the width, density, and direction of the Palomar 5 tidal tails}, 2019 (\arxiv{1910.00592})

\item[{\color{deemph}\scriptsize10}]Koppelman, H. H.; Helmi, A.; Massari, D.; \textbf{Price-Whelan,~A.~M.}~\textit{et al.}, \textit{Multiple retrograde substructures in the Galactic halo: A shattered view of Galactic history}, 2019 (\arxiv{1909.08924})

\item[{\color{deemph}\scriptsize9}]Smith, A. M.~\textit{et al.}~(incl. \textbf{APW}), \textit{Astro2020 APC White Paper: Elevating the Role of Software as a Product of the Research Enterprise}, 2019 (\arxiv{1907.06981})

\item[{\color{deemph}\scriptsize8}]Ness, M.~\textit{et al.}~(incl. \textbf{APW}), \textit{In Pursuit of Galactic Archaeology: Astro2020 Science White Paper}, 2019 (\arxiv{1907.05422})

\item[{\color{deemph}\scriptsize7}]Buckley, M. R.; Hogg, D. W.; \textbf{Price-Whelan,~A.~M.}, \textit{Applying Liouville's Theorem to Gaia Data}, 2019 (\arxiv{1907.00987})

\item[{\color{deemph}\scriptsize6}]Chakrabarti, S.; Chang, P.; \textbf{Price-Whelan,~A.~M.}; Read, J.~\textit{et al.}, \textit{Antlia2's role in driving the ripples in the outer gas disk of the Galaxy}, 2019 (\arxiv{1906.04203})

\item[{\color{deemph}\scriptsize5}]The MSE Science Team~\textit{et al.}~(incl. \textbf{APW}), \textit{The Detailed Science Case for the Maunakea Spectroscopic Explorer, 2019 edition}, 2019 (\arxiv{1904.04907}) [\href{http://adsabs.harvard.edu/abs/2019arXiv190404907T}{8 citations}]

\item[{\color{deemph}\scriptsize4}]Breivik, K.; \textbf{Price-Whelan,~A.~M.}; D'Orazio, D. J.; Hogg, D. W.~\textit{et al.}, \textit{Stellar multiplicity: an interdisciplinary nexus}, 2019 (\arxiv{1903.05094})

\item[{\color{deemph}\scriptsize3}]Bergemann, M.~\textit{et al.}~(incl. \textbf{APW}), \textit{Stellar Astrophysics and Exoplanet Science with the Maunakea Spectroscopic Explorer (MSE)}, 2019 (\arxiv{1903.03157})

\item[{\color{deemph}\scriptsize2}]\textbf{Price-Whelan,~A.~M.}; Nidever, D. L.; Choi, Y.; Schlafly, E. F.~\textit{et al.}, \textit{Discovery of a disrupting open cluster far into the Milky Way halo: a recent star formation event in the leading arm of the Magellanic stream?}, 2018 (\arxiv{1811.05991}) [\href{http://adsabs.harvard.edu/abs/2018arXiv181105991P}{5 citations}]

\item[{\color{deemph}\scriptsize1}]\textbf{Price-Whelan,~A.~M.}; Oh, S.; Spergel, D. N., \textit{Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from Gaia DR1}, 2017 (\arxiv{1709.03532}) [\href{http://adsabs.harvard.edu/abs/2017arXiv170903532P}{10 citations}]